---
title: "DATA419"
author: "Kayle Ransby", "Shuzhen Heng", "Zhihao Song", "Yun Chen", "Giulio Dalla Riva"
date: "19/05/2021"
output: pdf_document
---

Load the libraries we require.

```{r message=FALSE, warning=FALSE}

library(tidyverse)
library(tidygraph)
library(igraph)
library(ggraph)

```

Here we load the tweet data into the `tweet_dataframe` variable.

We intend on building the network based on the user_id, conversation_id and week variables; so filter out entries that have any of these variables empty.

```{r message=FALSE, warning=FALSE}

# Load tweet data
tweet_dataframe <- "Tweet file/tweets_cleaned_week.csv" %>%
  read_csv() %>%
  select(user_id, conversation_id, week) %>%
  filter(!is.na(user_id),
         !is.na(conversation_id),
         !is.na(week))

```

Here we are creating the links from the nodes (user_id) to the relations (conversation_id) as a bipartite network. We also include the week of the tweet for later on.

We need to be sure that we only include one of each link, as a single user may have been part of the same conversation multiple times.

```{r}

# Retrieve bipartite links from dataframe
bipartite_links <- tweet_dataframe %>%
  rename(to = user_id,from = conversation_id) %>%
  group_by(to, from, week) %>%
  slice(1) %>%
  ungroup()

```

Here we are converting from a bipartite to a unipartite network where users are linked to other users if they are part of the same conversation. The week variable here is based on the from column.

```{r}

# Generate network from links
user_links <- bipartite_links %>%
  full_join(bipartite_links, by = c("from", "week")) %>%   # we are full_joining links with links, and connecting them via the columns from and week
  filter(to.x != to.y) %>%                                 # we don't care about self links
  select(-from) %>%                                        # we only care about the users, not the tweets now
  rename(from = to.x, to = to.y) %>%                       # and we still want the from and to names for the columns
  group_by(to, from, week) %>%
  slice(1) %>%
  ungroup()

user_links <- user_links[, c('to', 'from', 'week')]        # change the order of the columns to make it easier to view

```

Here we are creating a graph object from the user_links dataframe for each week, identifying the communities using the Louvian method, then storing the node data in the `weekly_network_dataframe` variable.

```{r}

totalweeks <- 52     # Finishing week number

# dataframe list of the weekly network
weekly_network_dataframe <- data.frame(week=NA,
                                       name=NA,
                                       degree=NA,
                                       community=NA,
                                       transitivity=NA)

weekly_network_dataframe <- weekly_network_dataframe[FALSE,]

# Function to create a network at week n
week_n_network <- function(n) {
  
  user_links %>%
    filter(week == n) %>%      # Change the week you want to filter here
    graph_from_data_frame(directed = FALSE) %>%
    as_tbl_graph() %>%
    filter(!node_is_isolated()) %>%              # Filtering the isolated nodes
    mutate(community = group_louvain())          # Group the nodes into communities
  
}


#### Build weekly network, detect local communities by louvain method
for (n in 1:totalweeks){
  
  graph_data <- as_tibble(week_n_network(n))
  
  week <- rep(n, times = nrow(graph_data))
  
  # Save network to dataframe format
  weekly_network_dataframe <- rbind(weekly_network_dataframe, data.frame(week, graph_data))
  
}

```

find the father communities and son communities week by week by comparing the similarity of different community nodes.

```{r message=FALSE, warning=FALSE}

# Data frame that trace the community life line
community_trace <- data.frame(week = NA, 
                              community_id = NA, 
                              community_id_related = NA,
                              relationship_type = NA)

community_trace <- community_trace[FALSE,]

# Function to get the number of communities from a dataframe
get_number_of_communities <- . %>%
  select(community) %>% 
  max() %>%
  as.integer()

# Threshold for similarity between two communities
threshold <- 0.3

for (weeknum in 1:totalweeks) {
  
  # Get the number of communities for the current week
  current_num_comm <- weekly_network_dataframe %>%
    filter(week == weeknum) %>%
    get_number_of_communities()
    
  # Get the number of communities for the current week
  if (weeknum < totalweeks) {
    
    next_num_comm <- weekly_network_dataframe %>%
      filter(week == weeknum + 1) %>%
      get_number_of_communities()
    
  } else {
    
    next_num_comm <- 1
    
  }
  
  
  # Compare nodes in every community in current week and the week after
  for (current_comm in 1:current_num_comm) {  
    
    nodes_current_community <- weekly_network_dataframe %>% 
      filter(week == weeknum) %>%
      filter(community == current_comm) %>% 
      select(name)
    
    die_signal <- 0
    
    for (next_comm in 1:next_num_comm) {
      if (weeknum < totalweeks) {
        
        nodes_nextweek_community <- weekly_network_dataframe %>% 
          filter(week == weeknum+1) %>%
          filter(community == next_comm) %>% 
          select(name)
        
        ### Get the intersection of communities from current week and next week
        internodes <- intersect(nodes_current_community, nodes_nextweek_community)
        
        ### Calculate the proportion of intersection
        proportion <- count(internodes) / count(nodes_current_community)
        
        ### If proportion bigger than threshold:
        ### ---1, update the son_community for current week
        ### ---2, update the father_community value for next week community
        ### ---3, if it is the last week, finish the cooperation
        if (proportion >= threshold){
          
          son_row = c(weeknum, current_comm, next_comm, "s")       ## "s" stands for son_community_type
          father_row = c(weeknum+1, next_comm, current_comm, "f")  ## "f" stands for father_community_type
          community_trace[nrow(community_trace) + 1,] <- son_row
          community_trace[nrow(community_trace) + 1,] <- father_row
          
        }
        
        # Trace the result of intersection comparing
        if(proportion < threshold){
          
          die_signal <- die_signal + 1
          
        }
        
        # Put the dead community number in the father-son relationship,
        # if die_signal == next_num_comm, which means every community from next week has zero intersection with this current community.
        if (next_comm == next_num_comm & die_signal == next_num_comm){
          
          son_row = c(weeknum, current_comm, 0, "s")              ## "s" stands for son_community_type
          community_trace[nrow(community_trace) + 1,] = son_row
          
        }
      }
    }
  }
}

```

We now know what communities continue to live and which ones die. However there is no way to know currently if a community has been born (is new in the given week).

So we can now go through the `community_trace` dataframe and look for any communities that do not have fathers and give them a father of 0 (which means it was born this week).

```{r}

for (cweek in 1:totalweeks) { # loop over every week
  
  # Number of communities to look through
  num_comm <- weekly_network_dataframe %>%
    filter(week == cweek) %>%
    get_number_of_communities()
  
  # Look at the fathers for this week
  curr_fathers <- community_trace %>%
    filter(week == cweek) %>%
    filter(relationship_type == "f")
  
  for (comm in 1:num_comm) { # loop over every community
    
    if (!(comm %in% curr_fathers[,2])) {
      
      born_row <- c(cweek, comm, 0, "f")
      community_trace[nrow(community_trace) + 1,] = born_row
      
    }
  }
}

```

We now find the different predictors for each community, and create a dataframe containing a community, its predictors, its son (child community) and the som community's predictors.

```{r}

currentweek_precictors <- data.frame(y = NA,
                                     ave_degree = NA,
                                     transitivity = NA,
                                     motif_3_1 = NA,
                                     motif_3_2 = NA,
                                     motif_4_1 = NA,
                                     motif_4_2 = NA,
                                     motif_4_3 = NA,
                                     motif_4_4 = NA,
                                     motif_4_5 = NA,
                                     motif_4_6 = NA,
                                     density = NA,
                                     community_id = NA,
                                     week = NA)

nextweek_predictors <- data.frame(next_y = NA,
                                  next_ave_degree = NA,
                                  next_transitivity = NA,
                                  next_motif_3_1 = NA,
                                  next_motif_3_2 = NA,
                                  next_motif_4_1 = NA,
                                  next_motif_4_2 = NA,
                                  next_motif_4_3 = NA,
                                  next_motif_4_4 = NA,
                                  next_motif_4_5 = NA,
                                  next_motif_4_6 = NA,
                                  next_density = NA,
                                  next_community_id = NA)


currentweek_precictors <- currentweek_precictors[FALSE,]
nextweek_predictors <- nextweek_predictors[FALSE,]

### Only display the relationship by current community to son community, filter the "s" type relationship
expected_community_trace <- community_trace %>% 
  filter(relationship_type == "s") 

repvalue <- expected_community_trace %>%
  nrow() %>%
  as.numeric()

# function to get the predictors for the given week and community_id
get_week_predictors <- function(weeknum, community_id) {
  
  # Create a network for the current week and community
  current_community_net <- week_n_network(weeknum) %>%
    filter(community == community_id)
  
  # Average degree:
  ave_degree <- current_community_net %>%
    degree() %>%
    mean()
  
  # Transitivity:
  transitivity <- current_community_net %>%
    transitivity()
  
  if (is.nan(transitivity)) { # is NaN if no trangles are found, so set to 0
    transitivity <- 0
  }
  
  # Density
  density <- current_community_net %>%
    graph.density()
  
  # 3-motifs
  thr_motif <- current_community_net %>%
    motifs(3)
  
  thr_motif <- thr_motif[3:4] # Remove Na(s)
  
  # 4-motifs
  fou_motif <- current_community_net %>%
    motifs(4)
  
  fou_motif <- c(fou_motif[5], fou_motif[7:11]) # Remove Na(s)
  
  ## Expected y:
    
  # Number of edges
  exp_y <- current_community_net %>%
    igraph::gsize()
  
  # Number of nodes
  #exp_y <- current_community_net %>% 
  #  igraph::gorder()
  
  c(exp_y, ave_degree, transitivity, thr_motif, fou_motif, density)
}

for (n in 1:repvalue){
  
  # Get the current relationship's week number, community_id, son_community_id
  weeknum <- expected_community_trace[n,] %>%
    select(week) %>%
    as.integer()
  
  community_id <- expected_community_trace[n,] %>% 
    select(community_id) %>%
    as.integer()
  
  community_id_related <- expected_community_trace[n,] %>% 
    select(community_id_related) %>%
    as.integer()
  
  
  #### Current week:
  current_week <- c(get_week_predictors(weeknum, community_id), community_id, weeknum)
  currentweek_precictors[nrow(currentweek_precictors) + 1,] <- current_week
  
  
  #### Next week:
  if (!(community_id_related == 0)) { # If there is a related community
    
    next_week <- c(get_week_predictors(weeknum+1, community_id_related), community_id_related)
    nextweek_predictors[nrow(nextweek_predictors) + 1,] <- next_week
    
  } else { # the community is dead, set all predictors to 0
    
    next_week <- c(rep(0, times = 12), community_id_related)
    nextweek_predictors[nrow(nextweek_predictors) + 1,] <- next_week
    
  }
}

# Join the add-on column into father-son relationship data frame 
predictors <- data.frame(currentweek_precictors, nextweek_predictors)

```

Now we export these predictors as two separate .csv files

```{r}

write.csv(predictors, "predictors/predictors.csv", row.names = FALSE)

```

## From here on out, it's just plotting different things...

plot the whole network

```{r}

user_links %>% 
  ggraph(layout = 'stress') + 
  geom_edge_link(show.legend = FALSE) + 
  geom_node_point() +
  theme_graph()

```

plot the graph for a certain week.

```{r}

week = 1
week_n_network(week) %>%
  ggraph(layout = 'kk') + 
  geom_edge_link(show.legend = FALSE) + 
  geom_node_point(aes(color = as.factor(community)), size = 5) + 
  theme_graph()

```

Plot a single community from the given week

```{r}

week_n_network(week) %>%
  filter(community == 1) %N>%
  ggraph(layout = 'kk') + 
  geom_edge_link(show.legend = FALSE) + 
  geom_node_point(aes(color = as.factor(community)), size = 5) + 
  theme_graph()

```

Plot every week's graph in a .pdf file (Do not try to run this, it will not work for you)

```{r}

extrafont::loadfonts() # Prevents errors when building a pdf

pdf("visualisations/weeks_NZ.pdf")
for (week in 1:totalweeks) {
  plt <- week_n_network(week) %N>%
    ggraph(layout = 'kk') + 
    geom_edge_link(show.legend = FALSE) + 
    geom_node_point(aes(color = as.factor(community)), size = 5) + 
    theme_graph()
  print(plt)
}
dev.off()

```

Plot community time series

```{r}

communities <- c()    # Vector to store the number of communities in each week
born <- c()
dead <- c()
survive <- c()

for (inc in 1:totalweeks) {
  
  current_week <- community_trace %>%
    filter(week == inc)
  
  # get the number of born communities in the current week:
  tmp_born <- current_week %>%
    filter(relationship_type == 'f') %>%
    filter(community_id_related == 0) %>%
    dim()
  
  # get the number of dead communities in the current week:
  tmp_dead <- current_week %>%
    filter(relationship_type == 's') %>%
    filter(community_id_related == 0) %>%
    dim()
  
  
  # get the number of communities that continue on to the next week:
  tmp_cont <- current_week %>%
    filter(relationship_type == 's') %>%
    filter(community_id_related != 0) %>%
    dim()
  
  
  # Calculate the number of communities in the current week:
  tmp_comm <- weekly_network_dataframe %>%
    group_by(week, community) %>%
    slice(1) %>%
    ungroup() %>%
    filter(week == inc) %>%
    data.frame() %>%
    summarise(community)

  communities[inc] <- length(tmp_comm$community)
  born[inc] <- tmp_born[1]
  dead[inc] <- tmp_dead[1]
  survive[inc] <- tmp_cont[1]
  
}


# Create a dataframe using the four vectors
data <- data.frame(week = rep(seq(1:52), times = 4),
                 type = rep(c("Total", "Born", "Dead", "Survive"), each = 52),
                 measures = c(communities, born, dead, survive))

# Create a plot showing the different measures by week
p <- ggplot(data, aes(x = week, y = measures, group = type)) +
  ggtitle("Time series for communities") +
  geom_smooth(formula = y ~ x, method = "loess", fill = NA, aes(color = type))

# Show the plot
p

```

Save the plot as an svg:

```{r}

# Save the plot as a .svg file
svg("visualisations/community_time_series.svg", width = 10, height = 6)
p
dev.off()

```

